\chapter{Statistics}
\label{stat}

\section{ What is the average daily range.}
\section{ What is the average daily volume.}
\section{ What would you define as a low volume days?}
\section{ What is the average weekend range.}
\section{ What affect does an increase in open interest have on price?}
\section{ What affect does a decrease in open interest have on price?}
\section{ Does any relationship exist between open interest and price?}
\section{ What is the average session range and volume - asia euro usa.}
\section{ Work out the ATR of Eth in excel and read the ATR pdf.}
\section{ Work out the distribution of returns and read the pdf.}
\section{ What is the most common time of day for price movements.}
\section{ What are the most common times with the most volume.}
\section{ Is beginning of the month typically quieter then end of month?}
\section{ List of days where it trades greater then its Standard deviation, check (1SD, 2SD, 3SD)}
\section{ Is the market more likely to go up or down?}

\section{ How does the market move when it is $>5  \%  $ move in a day}
\section{ How does the market move when its $>10 \% $ in a day}
\section{ How does it move when its under $<5 \% $?}
\section{ What are the days before and after like of both $>5 \% $ and $<5 \% $ and $> 10 \% $}
\section{ Does it tend to trend or range more?}
fdlgjlskdjgvsdgvdsvsadvfgasdvf
\section{ Do stationary test}
\section{If you used the POC as the fair value for the next trading day, how often does price come back to test this area? (Point of Control)}
\section{Does over average in volume generally relate to bigger price movements? Does this generally last for more then one day?}
\section{Average transactions on the network per day}
\section{Does increase in transactions increase demand and price?}