\chapter{Technical}
\label{tech}

\section{ What is the average size of a move: Small, medium, large.}
\section{ Most amount of candles in a row with one color}
\section{ Does the market respond to triangles / wedges?}
\section{ Does the market respond to flags? bull flags vs bear flags, flat flags. }
\section{ Are double top / bottoms good? are head and shoulders patterns good?}
\section{ Ascending channel vs descending channels}
\section{ Does the market fill the CME gap from the weekends trading? If so what are some statistics around this?}
\section{ Are weekends more likely to trend or range?}
\section{ How does changes in volume affect the market}
\section{ Does volatility drop and volume drop at the same time or do they move inline}
\section{ Do liquidations occur with or against the trend}
\section{ When it ranges how big are the moves and what size reversions do they have?}
\section{ When it goes quiet what sort of ranges and volumes does it do right before a big move?}
\section{ When we have days of abnormally low volume what type of days do we see after this?}
\section{ Once it has a big move (define this) what does the following 5 days look like}
\section{ What does the next 12, 24 hours look like after a large move?}
\section{ Are moves more likely to retrace or continue on longs or shorts?}
\section{ Look into what vwap is, put it on your chart and see does vwap work? is it more active in ranging or trending, more volatile or less volatile.}
\section{ Are the euro sessions more prone to reverse or continue the move?}
\section{ Are the usa sessions more prone to reverse or continue the move?}
\section{ How responsive is the market to current SFL levels? (tradingview)}
\section{ Which SFL levels are the most important? }
\section{ Does price respect past SFL levels?}